Using traffic analysis to identify The Second Generation Onion Router

### 2011-06-13 ieee-conference-paper/paper.tex
Added three references I hadn't already used to emphasise wealth of the literature

While Tor has been the subject of much academic literature, the primary
objective of researchers has historically been the attempt to reveal participant
identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques proposed
have been somewhat academic in nature and not necessarily feasible in practice
\parencite{Raccoon:2008fk}. In certain circumstances they require compromise of
large parts of the Tor network, supplying hostile data to Tor users or
complicated knowledge of usage patterns and an excess of patience. The
technique demonstrated in this paper is a low cost technique, which does not
require sophisticated equipment and can be completed by a passive observer.

>>>>

While Tor has been the subject of much academic literature
\parencite{Hopper:2007p347,Murdoch:2007p320,Herrmann:2009p1189}, the primary
objective of researchers has historically been the attempt to reveal
participant identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques
proposed have been somewhat academic in nature and not necessarily feasible in
practice \parencite{Raccoon:2008fk}. In certain circumstances they require
compromise of large parts of the Tor network, supplying hostile data to Tor
users or complicated knowledge of usage patterns and an excess of patience. The
technique demonstrated in this paper is a low cost technique, which does not
require sophisticated equipment and can be completed by a passive observer.
